Bad forecast, good decision: accuracy can be a poor metric for policy

### 2020-09-15 manuscript/manuscript.Rmd
:pen:

While in principle the utility could reflect many things, including the cost of fishing, market responses to supply and demand, the value of recreational fishing, the intrinsic value fish left in the sea [see @Halpern], for simplicity we will assume utility is merely a linear function of the harvest, i.e. a fixed price $p$ per kilogram of fish harvested: $U(X_t, H_t) = p H_t$. This problem is already well studied, and it is worth noting that even under such a pessimistic assumption, the optimal strategy still seeks to sustain the fish population indefinitely; as @Clark1974 shows for the deterministic function $f$ and @Reed1979 extended to the stochastic case. Given the function $f$ with known parameters, it is straight forward to determine the optimal harvest policy by stochastic dynamic programming (SDP, see @Mangel; @Marescot2013).

>>>>

While in principle the utility could reflect many things, including the cost of fishing, market responses to supply and demand, the value of recreational fishing, the intrinsic value fish left in the sea [see @Halpern2013], for simplicity we will assume utility is merely a linear function of the harvest, i.e. a fixed price $p$ per kilogram of fish harvested: $U(X_t, H_t) = p H_t$. This problem is already well studied, and it is worth noting that even under such a pessimistic assumption, the optimal strategy still seeks to sustain the fish population indefinitely; as @Clark1973 shows for the deterministic function $f$ and @Reed1979 extended to the stochastic case. Given the function $f$ with known parameters, it is straight forward to determine the optimal harvest policy by stochastic dynamic programming (SDP, see @Mangel1985; @Marescot2013).
